%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\hypersetup{
colorlinks=true,
urlcolor=blue
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-1pt}}
  }
}

\newcommand{\workItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-0.6pt}}
  }
}

\newcommand{\resumeCoding}[1]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \\      
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4.6pt}}
\newcommand{\resumeItemWorkDoneListStart}{\begin{itemize}}
\newcommand{\resumeItemWorkDoneListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{/}{\Large Erik-Cristian Seulean}} & 
    Email : \href{mailto:erikseulean@gmail.com}{erikseulean@gmail.com}\\ & 
    Mobile : +44-780-496-3809\\ &
    \href{https://www.linkedin.com/in/erikseulean/}{linkedin.com/in/erikseulean/}
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of St. Andrews}{United Kingdom}
      {MSc Statistics} {Distinction, Deans' List, grade 17.9/20, September 2022}
    \resumeItemListStart
    	\resumeItem{Modules}
        {Markov Chains, Bayesian Statistics, Multivariate Analysis, Statistical Modelling using GLM/GAMs, Quantitative risk analysis, Machine Learning}
      \resumeItem{Dissertation}
        {An Ensemble of HMM and KNN for signal generation in horse betting markets. Grade 19.3/20 - Highest grade in my cohort}   
    \resumeItemListEnd
    \resumeSubheading
      {University of Sheffield}{Remote, United Kingdom}
      {Graduate Certificate in Statistics}{Distinction, grade 90/100, July 2021}
    \resumeItemListStart
    	\resumeItem{Modules}
        {Mathematical Methods for Statistics, Probability and Probability Distributions, Basic Statistics}
    \resumeItemListEnd
    \resumeSubheading
      {Politechnica University of Timisoara}{Timisoara, Romania}
      {B.S.E in Computer Science}{July, 2014}
    \resumeItemListStart
    	\resumeItem{Modules}
        {Software Engineering, Computer Architecture, Algorithms, Software Development Fundamentals, Design Patterns, Programming Languages, Databases}
    \resumeItemListEnd        
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bloomberg LP}{London, United Kingdom}
      {Senior Software Engineer}{2019 - September 2021}
      \resumeItemListStart
        \resumeItem{Taxonomy and Metadata System}
          {Infrastructure team developing a taxonomy and metadata system to support various asset classes at Bloomberg. Python, GraphQL, Redis, RabbitMQ, Solr, RDF, PostgreSQL, Data Pipeline}
          \resumeItemListStart
            \workItem{}
              {\textbf{Architected ingestion pipelines} that handle ingestion of metadata for datasets such as commodity index tickers.}
            \workItem{}
              {Added \textbf{support for sharding} to increase the speed of the ingestion pipeline. Split up the initial ingestion into 8 shards that are running distributed across an entire cluster.}
              \workItem{}
              {Implemented node overlay and concatenation executed on RDF graphs.}
              \workItem{}
              {Worked on \textbf{rearchitecting the ingestion pipeline} from a synchronous pipeline to a file based ingestion.}
              \workItem{}
              {Migrated the codebase from Python 2 to Python 3 \textbf{decreasing the overall response time of services by 15}\%}
              \workItem{}
              {Implemented services in GraphQL to avoid overfetching and underfetching on the existing Bloomberg specific microservice framework.}
              \workItem{}
              {Led \textbf{intergration of the metadata system with timeseries datasets}, a company wide effort to support non-tickerized data.}              
              \workItem{}
              {Worked on a side project, debugging tool, to help find metadata for given entities regardless of the source of provenience, using a \textbf{topological sort algorithm on service APIs and RDF Graphs}.}
              \workItem{}
              {Led the \textbf{research into adoption of triplestores} at Bloomberg, an effort across 6 departments towards choosing the right solution to cover the usecases presented at Bloomberg. Researched on solutions such as Virtuoso or TerminusDB.}
              \workItem{}
              {Organized weekly department-wide design discussions, to share knowledge regarding ongoing work.}
              \workItem{}
              {Team lead backup for a team of 7 engineers.}
          \resumeItemListEnd
        \resumeItemListEnd
      \resumeSubheading
        {Bloomberg LP} {London, United Kingdom}
        {Software Engineer}{2016 - 2019}
      \resumeItemListStart
        \resumeItem{Real Time Analytics}
          {Application team, maintaining a large variety of analytics, integrated in different products across Bloomberg. Processing several billion trades per day. C++, Distributed, Realtime}
          \resumeItemListStart
            \workItem{}
              {Implemented Average Volume at Time for non equities and Top Exchanges in the past X minutes.} 
            \workItem{}
              {Implemented a \textbf{load testing facility} that is used to simulate the impact of market open on the system to assess performance and capacity. I identified a bottleneck in the system and by fixing it, subscriptions are being processed 3 times faster.}
    		\workItem{}
              {\textbf{Increased availability} of an analytic by implementing fallback to disk in case the database connection cannot be established. This prevents the 1 minute downtime per week when the database cluster is being rebooted.}
          \resumeItemListEnd
        \resumeItem{Recommendation Disclosures and Trade Ideas}
        {Python, Typescript, Microservices, Event Sourcing}
        \resumeItemListStart
          \workItem{}
              {Implemented asynchronous messaging using RabbitMQ to allow distribution of recommendations. Added support to publish messages, implemented consumers and set up the middleware.}
          \workItem{}
            {Reduced the codebase by 8\% by removing around 100.000 lines of dead or unused code.}            
        \resumeItemListEnd
      \resumeItemListEnd    
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \resumeCoding {Coding}
      \resumeItemListStart
        \resumeItem {attrs-strict https://github.com/bloomberg/attrs-strict}
        {Created and open-sourced a library that allows runtime validation for attrs dataclasses in Python.}
        \resumeItem {bloomberg-bas-middleware}
        {Maintainer and creator of an inner source library used for Python services at Bloomberg. Created Flask-like middlewares that are used in over 10.000 services running in Python 3 at Bloomberg. Any new service has by default the functionality opted-in.}
        \resumeItem {Python Guild}
        {Part of a group of 18 engineers leading the direction and adoption of Python at Bloomberg, led the Design Reviews Working group, helping teams to bring projects to a broader audience.}
        \resumeItem {ML 101}
        {Participated in a 6 month hands on Machine Learning training. The timeseries clustering project developed in a team of 3 was one of the 2 projects out of 15 to be showcased in front of senior management at Bloomberg.}  
      \resumeItemListEnd
    \resumeCoding {Public speaking for large audiences}
      \resumeItemListStart
        \workItem{}
        {\textbf{"How to migratate services to Python 3"} -  Attendance of over 200 engineers.}
        \workItem{}
        {\textbf{"Modeling the commodity world"} - Presentation on the architecture of the system I worked on and the different architectural decisions taken in the past years. Attendance of over 150 engineers.}
      \resumeItemListEnd
    \resumeCoding {Mentorship}
      \resumeItemListStart
        \workItem{}
        {Mentored in workshops to help engineers migrate their services to Python 3.}
        \workItem{}
        {Mentored an intern during the summer internship program.}
        \workItem{}
        {Mentored new joiners in the team and helped people contribute to inner-source projects at Bloomberg}
      \resumeItemListEnd
   \item{
     \textbf{Architecture and technology}{: Large scale distributed systems, Data pipelines, Microservices, GraphQL, PostgreSQL, Redis, Solr, RabbitMQ, Event Sourcing, Git, RDF}
   }
   \item{
     \textbf{Languages}{: Python, Javascript, Typescript, SQL, C\#}
   }
   \item{
     \textbf{Mathematics}{: Probability theory, Markov chains, Bayesian models, GLMs, statistical inference}
   }
   \item{
     \textbf{Machine Learning}{: Regression, Trees, Ensemble Methods, Boosting, Neural networks, unsupervised learning}
   }
   \item{
     \textbf{Languages spoken}{: I speak English(IELTS Grade 8.0) and Romanian fluently. Currently living in London.}
   }   	
 \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Personal Projects}
  \resumeSubHeadingListStart
    \resumeSubItem {G-Research speed coding challenge}
    {(October 2021) Second place in Scotland at the university coding challenge organised by G-Research. Competed against teams of 4.}
    \resumeSubItem {Cryptocurrency analysis https://github.com/erikseulean/cryptoscraping}
    {(January 2018) Scraped cryptocurrency data from different sources and created a library that allows to easily analyse prices, market cap and volume. I implemented and plotted the Ichimoku indicator and created correlation plots between google trends and different cryptocurrencies. Python: Numpy, Pandas, Matplotlib, Multiprocessing, Jupyter}
    \resumeSubItem{ColorBlocks}
      {(November 2015) Awarded 2nd prize competing against 12 teams at HackTM, the largest Hackathon in Eastern Europe lasting 50 hours straight. I was part of a team of three and we developed a cross-platform puzzle game for mobile and tablet devices. Available on Google Play as ColorBlocks. LUA}
    \resumeSubItem{Cycling Community Platform}
    	{(October 2012) Awarded 2nd prize competing against 20 teams in Microsoft Excite, three week competition. Developed a mobile and web based platform for the local cycling community. I was part of a team of three students. C\#.NET, Javascript, SQL}
  \resumeSubHeadingListEnd

\end{document}
