%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\hypersetup{
colorlinks=true,
urlcolor=blue
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\workItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-1.5pt}}
  }
}

\newcommand{\resumeCoding}[1]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-6pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}
\newcommand{\resumeItemWorkDoneListStart}{\begin{itemize}}
\newcommand{\resumeItemWorkDoneListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{/}{\Large Erik-Cristian Seulean}} & 
    Email : \href{mailto:erikseulean@gmail.com}{erikseulean@gmail.com}\\ & 
    Mobile : +44-780-496-3809\\ &
    \href{https://www.linkedin.com/in/erikseulean/}{linkedin.com/in/erikseulean/}\\ &
    Citizenship: British, Romanian, Hungarian
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Citadel (Fixed Income and Macro)}{London, United Kingdom}
      {Senior Software Engineer $\to$ Engineering Manager}{April 2023 - Present}
      \resumeItemListStart
        \resumeItem{Research Data Platform (Storage \& API Layer)}
          {}
          \resumeItemListStart
            \workItem{}
              {Sole architect and developer of a centralized research data platform, now adopted by \textbf{all systematic desks}}
            \workItem{}
              {Built on \textbf{PostgreSQL and Arrow Flight} over gRPC with bidirectional streaming APIs directly from database cursors; deployed on \textbf{Kubernetes}}
            \workItem{}
              {Introduced sharded per-desk architecture for independent scalability, enabling heavy-usage teams to run their own stacks, with built-in permissions and TTLs to protect desk-specific IP and restrict the growth of unused data}
            \workItem{}
              {Designed and implemented the research storage API, which became the preferred interface for department-wide data access, prompting migration of other storage systems to use this API due to its intuitive design and streamlined workflow}
          \resumeItemListEnd
        \resumeItem{Market Data Infrastructure (Tick Pipeline)}
          {}
          \resumeItemListStart
            \workItem{}
              {Sole developer of a tick data ingestion pipeline ingesting data from multiple market venues in real time, processing \textbf{30B+ market events/day} across \textbf{27M+ unique instruments}}
            \workItem{}
              {Built a low-latency, high-throughput system using \textbf{Kafka, Redis, and C++} with concurrent and lock-free design patterns; \textbf{primary expertise is in system design and Python-based data engineering}}
            \workItem{}
              {Designed for production resilience, scalable for increased market data needs, and seamlessly rolled out without disruptions to existing usecases}
          \resumeItemListEnd
        \resumeItem{Leadership \& Platform Transformation}
          {}
          \resumeItemListStart
            \workItem{}
              {\textbf{Promoted to Engineering Manager}, leading two teams (6 engineers) focused on data onboarding and data platform infrastructure}
            \workItem{}
              {Modernized the data onboarding platform, overseeing migration of \textbf{5,000+ ETL jobs} and reducing onboarding times from 5+ months to \textbf{$<$30 days}}
            \workItem{}
              {Architecting and leading the team developing a department-wide data quality and discovery platform, providing validation checks, dataset health monitoring, metadata management, multi-storage support, and data arbitration}
          \resumeItemListEnd
        \resumeItemListEnd
    \resumeSubheading
      {University of St. Andrews}{United Kingdom}
      {Career break for full-time study (details in Education section)}{September 2021 - September 2022}
    \resumeSubheading
      {Bloomberg LP}{London, United Kingdom}
      {Senior Software Engineer}{2019 - September 2021}
      \resumeItemListStart
        \resumeItem{Taxonomy and Metadata System}
          {Infrastructure team developing a taxonomy and metadata system to support various asset classes at Bloomberg. Python, GraphQL, Redis, RabbitMQ, Solr, RDF, PostgreSQL, Data Pipeline}
          \resumeItemListStart
            \workItem{}
              {\textbf{Architected ingestion pipelines} that handle ingestion of metadata for datasets such as commodity index tickers.}
            \workItem{}
              {Added \textbf{support for sharding} to increase the speed of the ingestion pipeline. Split up the initial ingestion into 8 shards that are running distributed across an entire cluster.}
              \workItem{}
              {Implemented node overlay and concatenation executed on RDF graphs.}
              \workItem{}
              {Worked on \textbf{rearchitecting the ingestion pipeline} from a synchronous pipeline to a file based ingestion.}
              \workItem{}
              {Implemented services in GraphQL to avoid overfetching and underfetching on the existing Bloomberg specific microservice framework.}
              \workItem{}
              {Worked on a side project, debugging tool, to help find metadata for given entities regardless of the source of provenience, using a \textbf{topological sort algorithm on service APIs and RDF Graphs}.}
              \workItem{}
              {Team lead backup for a team of 7 engineers.}
          \resumeItemListEnd
        \resumeItemListEnd
      \vspace{2pt}
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small Software Engineer} & \textit{\small 2016 - 2019} \\
      \end{tabular*}\vspace{-6pt}
      \resumeItemListStart
        \resumeItem{Real Time Analytics}
          {Application team, maintaining a large variety of analytics, integrated in different products across Bloomberg. Processing several billion trades per day. C++, Distributed, Realtime}
          \resumeItemListStart
            \workItem{}
              {Implemented Average Volume at Time for non equities and Top Exchanges in the past X minutes.} 
            \workItem{}
              {Implemented a \textbf{load testing facility} that is used to simulate the impact of market open on the system to assess performance and capacity. I identified a bottleneck in the system and by fixing it, subscriptions are being processed 3 times faster.}
    		\workItem{}
              {\textbf{Increased availability} of an analytic by implementing fallback to disk in case the database connection cannot be established. This prevents the 1 minute downtime per week when the database cluster is being rebooted.}
          \resumeItemListEnd
        \resumeItem{Recommendation Disclosures and Trade Ideas}
        {Python, Typescript, Microservices, Event Sourcing}
        \resumeItemListStart
          \workItem{}
              {Implemented asynchronous messaging using RabbitMQ to allow distribution of recommendations. Added support to publish messages, implemented consumers and set up the middleware.}
          \workItem{}
            {Reduced the codebase by 8\% by removing around 100.000 lines of dead or unused code.}            
        \resumeItemListEnd
      \resumeItemListEnd
      \resumeSubheading
        {Intelligent Software Systems} {Timisoara, Romania}
        {Software Engineer}{2013 - 2016}
        \resumeItemListStart
          \workItem{}
          {Built a desktop-to-CRM sync tool (workbooks.com) and contributed features and bug fixes to the FAFSA questionnaire.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of St. Andrews}{United Kingdom}
      {MSc Statistics} {Distinction, Deans' List, grade 17.9/20, September 2022}
    \resumeItemListStart
    	\resumeItem{Modules}
        {Markov Chains, Bayesian Statistics, Multivariate Analysis, Statistical Modelling using GLM/GAMs, Quantitative risk analysis, Machine Learning}
      \resumeItem{Dissertation}
        {An Ensemble of HMM and KNN for signal generation in horse betting markets. Grade 19.3/20 - Highest grade in my cohort}
    \resumeItemListEnd
    \resumeSubheading
      {University of Sheffield}{Remote, United Kingdom}
      {Graduate Certificate in Statistics}{Distinction, grade 90/100, July 2021}
    \resumeItemListStart
    	\resumeItem{Modules}
        {Mathematical Methods for Statistics, Probability and Probability Distributions, Basic Statistics}
    \resumeItemListEnd
    \resumeSubheading
      {Politechnica University of Timisoara}{Timisoara, Romania}
      {B.S.E in Computer Science}{July, 2014}
    \resumeItemListStart
    	\resumeItem{Modules}
        {Software Engineering, Computer Architecture, Algorithms, Software Development Fundamentals, Design Patterns, Programming Languages, Databases}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \resumeCoding {Coding}
      \resumeItemListStart
        \resumeItem {attrs-strict https://github.com/bloomberg/attrs-strict}
        {Created and open-sourced a library that allows runtime validation for attrs dataclasses in Python.}
        \resumeItem {bloomberg-bas-middleware}
        {Maintainer and creator of an inner source library used for Python services at Bloomberg. Created Flask-like middlewares that are used in over 10.000 services running in Python 3 at Bloomberg. Any new service has by default the functionality opted-in.}
        \resumeItem {Python Guild}
        {Part of a group of 18 engineers leading the direction and adoption of Python at Bloomberg, led the Design Reviews Working group, helping teams to bring projects to a broader audience.}
      \resumeItemListEnd
    \resumeCoding {Public speaking for large audiences}
      \resumeItemListStart
        \workItem{}
        {\textbf{"How to migratate services to Python 3"} -  Attendance of over 200 engineers.}
        \workItem{}
        {\textbf{"Modeling the commodity world"} - Presentation on the architecture of the system I worked on and the different architectural decisions taken in the past years. Attendance of over 150 engineers.}
      \resumeItemListEnd
    \resumeCoding {Mentorship}
      \resumeItemListStart
        \workItem{}
        {Mentored interns and junior/mid engineers at Citadel and Bloomberg, conducted interviews, ran workshops on Python 3 migration, and supported new joiners in ramping up and contributing to inner-source projects.}
      \resumeItemListEnd
   \item{
     \textbf{Architecture and technology}{: Large scale distributed systems, Data pipelines, Microservices, GraphQL, PostgreSQL, Redis, Kafka, Solr, RabbitMQ, Event Sourcing, Git, RDF}
   }
   \item{
     \textbf{Data onboarding}{: External data ingestion via APIs, SFTP, web scraping and PDF parsing; sources include Bloomberg (PerSecurity/BLPAPI), Refinitiv, S\&P; ETL pipeline management at scale}
   }
   \item{
     \textbf{Languages}{: Python (primary), C++ (production use), JavaScript/TypeScript (basic), SQL}
   }
   \item{
     \textbf{Mathematics}{: Probability theory, Markov chains, Bayesian models, GLMs, statistical inference}
   }

 \resumeSubHeadingListEnd


\end{document}
