%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\hypersetup{
colorlinks=true,
urlcolor=blue
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-1pt}}
  }
}

\newcommand{\workItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-0.6pt}}
  }
}

\newcommand{\resumeCoding}[1]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \\      
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4.6pt}}
\newcommand{\resumeItemWorkDoneListStart}{\begin{itemize}}
\newcommand{\resumeItemWorkDoneListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{/}{\Large Erik-Cristian Seulean}} & 
    Email : \href{mailto:erikseulean@gmail.com}{erikseulean@gmail.com}\\ & 
    Mobile : +44-780-496-3809\\ &
    \href{https://www.linkedin.com/in/erikseulean/}{linkedin.com/in/erikseulean/}
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Citadel Asset Management}{London, United Kingdom}
      {Data Engineer $\to$ Engineering Manager}{2022 - Present}
      \resumeItemListStart
        \resumeItem{Market Data Infrastructure (Tick Pipeline)}{}
          \resumeItemListStart
            \workItem{}
              {Sole developer and owner of a department-wide tick data pipeline processing \textbf{30B+ market events per day}.}
            \workItem{}
              {Built a \textbf{low-latency, high-throughput} ingestion system in C++, Kafka, and Redis, leveraging concurrent and lock-free design patterns.}
            \workItem{}
              {Designed for resilience under peak market conditions: \textbf{zero-downtime rollout} and no production outages over 3+ years.}
            \workItem{}
              {Core market data feed powering research and trading workflows across the department.}
          \resumeItemListEnd
        \resumeItem{Research Data Platform (Storage \& API Layer)}{}
          \resumeItemListStart
            \workItem{}
              {Sole architect and developer of the central research data platform, \textbf{adopted by 25 of 40 systematic trading desks} ($\sim$60\%).}
            \workItem{}
              {Built on \textbf{PostgreSQL and Arrow Flight}, enabling high-performance bidirectional streaming APIs for large-scale data access.}
            \workItem{}
              {Implemented streaming reads/writes directly from database cursors, reducing memory overhead and improving throughput.}
            \workItem{}
              {Became the de facto standard for systematic research, \textbf{driving migration of all existing internal data APIs}.}
          \resumeItemListEnd
        \resumeItem{Leadership \& Platform Transformation}{}
          \resumeItemListStart
            \workItem{}
              {\textbf{Promoted from IC to Engineering Manager} within 3 years while continuing to own and ship production infrastructure.}
            \workItem{}
              {Leading \textbf{two teams (6 engineers)} across data onboarding and platform development.}
            \workItem{}
              {Reduced data onboarding time from \textbf{5+ months to under 30 days}, significantly accelerating dataset availability for research.}
            \workItem{}
              {Oversaw migration of \textbf{5,000+ ETL jobs}, standardising ingestion and reducing operational complexity.}
            \workItem{}
              {Offered the role of \textbf{Head of Data Engineering} for the department, expanding scope to a third team and full ownership of the data engineering function.}
          \resumeItemListEnd
      \resumeItemListEnd
    \resumeSubheading
      {Bloomberg LP}{London, United Kingdom}
      {Senior Software Engineer}{2019 - 2021}
      \resumeItemListStart
        \resumeItem{Taxonomy and Metadata System}
          {Python, GraphQL, Redis, RabbitMQ, PostgreSQL, Data Pipeline}
          \resumeItemListStart
            \workItem{}
              {\textbf{Architected ingestion pipelines} handling metadata for large-scale datasets across multiple asset classes, including commodity index tickers and non-tickerized financial instruments.}
            \workItem{}
              {Added \textbf{support for sharding} to the ingestion pipeline, splitting work across 8 distributed shards and significantly increasing throughput.}
            \workItem{}
              {Led \textbf{cross-department integration of the metadata system with timeseries datasets}, enabling unified access to structured financial data across asset classes — a company-wide initiative spanning 6 teams.}
            \workItem{}
              {Team lead backup for a team of 7 engineers.}
          \resumeItemListEnd
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of St. Andrews}{United Kingdom}
      {MSc Statistics} {Distinction, Deans' List, grade 17.9/20, September 2022}
    \resumeItemListStart
    	\resumeItem{Modules}
        {Markov Chains, Bayesian Statistics, Multivariate Analysis, Statistical Modelling using GLM/GAMs, Quantitative risk analysis, Machine Learning}
      \resumeItem{Dissertation}
        {An Ensemble of HMM and KNN for signal generation in horse betting markets. Grade 19.3/20 --- Highest grade in cohort}
    \resumeItemListEnd
    \resumeSubheading
      {University of Sheffield}{Remote, United Kingdom}
      {Graduate Certificate in Statistics}{Distinction, grade 90/100, July 2021}
    \resumeItemListStart
    	\resumeItem{Modules}
        {Mathematical Methods for Statistics, Probability and Probability Distributions, Basic Statistics}
    \resumeItemListEnd
    \resumeSubheading
      {Politechnica University of Timisoara}{Timisoara, Romania}
      {B.S.E in Computer Science}{July 2014}
    \resumeItemListStart
    	\resumeItem{Modules}
        {Software Engineering, Computer Architecture, Algorithms, Design Patterns, Programming Languages, Databases}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Open Source}{: \href{https://github.com/bloomberg/attrs-strict}{attrs-strict} --- runtime validation library for Python attrs dataclasses, created and open-sourced at Bloomberg.}
   }
   \item{
     \textbf{Architecture and technology}{: Large-scale distributed systems, data pipelines, C++, Kafka, Redis, Arrow Flight, PostgreSQL, Python, gRPC, Airflow, lock-free concurrency}
   }
   \item{
     \textbf{Mathematics}{: Probability theory, Markov chains, Bayesian models, GLMs, statistical inference}
   }
   \item{
     \textbf{Languages spoken}{: English (IELTS 8.0), Romanian (native). Currently living in London.}
   }
  \item{
    \textbf{Citizenships}{: British, Romanian, Hungarian}
  }
 \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Personal Projects}
  \resumeSubHeadingListStart
    \resumeSubItem {G-Research speed coding challenge}
    {(October 2021) Second place in Scotland at the university coding challenge organised by G-Research. Competed against teams of 4.}
    \resumeSubItem {Cryptocurrency analysis \href{https://github.com/erikseulean/cryptoscraping}{github.com/erikseulean/cryptoscraping}}
    {(January 2018) Scraped cryptocurrency data from multiple sources; implemented the Ichimoku indicator and correlation analysis between Google Trends and crypto prices. Python: Numpy, Pandas, Matplotlib, Multiprocessing, Jupyter.}
  \resumeSubHeadingListEnd

\end{document}
